Ensuring Fairness with Transparent Auditing of Quantitative Bias in AI Systems\\ \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-05-25 paper/abstract.tex
Added plt images

For the legitimate predicate, we may want to look at defendants with priors.
\[
    \leg(x)(r_i) := \mathtt{int}(r_i(\text{``priors\_count''})) > x
\]

For the score predicate, we may want to specifically look at risk scores between a specifically range.
\[
    \sco(u,l)(r_i) := l \leq \mathtt{int}(r_i(\text{``decile\_score''})) \leq u
\]

@@

We can then immediately tell from it failing demographic parity, mean difference, and conditional statistical parity that COMPAS prediction results was unfair against African-American, even if we only consider the ones with prior crimes.

@@

From failing both equalized odds criteria we can conclude that African-Americans are indeed treated unequally by the COMPAS system even after the ground truth is taken into account. This is the same conclusion reached by the ProPublica report.

From the low equal calibration we can tell that if we only consider the medium risk score, African-Americans aren't treated unequally.

>>>>

For the legitimate predicate, we may want to look at defendants with priors. Here we shall set $args = (0)$.
\[
    \leg(x)(r_i) := \mathtt{int}(r_i(\text{``priors\_count''})) > x
\]

For the score predicate, we may want to specifically look at risk scores between a specifically range. Here we shall set $args = (7,5)$.
\[
    \sco(u,l)(r_i) := l \leq \mathtt{int}(r_i(\text{``decile\_score''})) \leq u
\]

@@

We can then immediately tell from the failing demographic parity, mean difference, and conditional statistical parity that COMPAS prediction results was unfair against African-American, even if we only consider the ones with prior crimes.

@@

From the failing equalized odds we can conclude that African-Americans are indeed treated unequally by the COMPAS system even after the ground truth is taken into account. This is the same conclusion reached by the ProPublica report.

From the low equal calibration we can tell that if we only consider the medium risk score, African-Americans aren't treated fairly.
